---
title: 'Week 2 Assignment: DC Area Ski Resorts'
---
title: "Week 2 Assignment: My Favorite Ski Areas in the Washington D.C. Metro Area"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Create a web page using R Markdown that features a map created with Leaflet. Host your webpage on either GitHub Pages, RPubs, or NeoCities.  

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Review criteria
The rubric contains the following two questions:

  1. Does the web page feature a date and is this date less than two months before 
     the date that you're grading this assignment?

  2. Does the web page feature an interactive map that appears to have been 
     created with Leaflet?

## Leaflet Map
Click on the markers to get the resort name,

```{r}
library(leaflet) 

ski_areas <- data.frame(lat = c(39.74167, 40.1095, 39.7637, 39.5569, 39.0425, 
                                38.4030),
                 lng = c(-77.93278, -76.9275, -77.3755, -79.3634, -79.3990, 
                         -79.9939))

resorts <- c("Whitetail Resort", "Roundtop Mountain Resort", "Liberty Mountain Resort",
             "Wisp Resort", "Timberline Mountain Resort", "Snoeshoe Mountain Resort")

ski_areas %>% 
    leaflet() %>%
    addTiles() %>%
    addMarkers(popup = resorts)
```
